### 2016-07-06 version0.0/comprehensive_exam.tex
adding prelude to into. section

\section{Overview}

Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe. Stars are also central to the formation of planetary systems and are where the ingredients for life were formed. The energy provided by stars is necessary to maintain the life on planets. The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System. This is one of the main reasons that the study of stellar structure and evolution has been a central topic in astronomy and astrophysics for decades.

@@

In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the interstellar medium (ISM) which is due to gravitational instabilities. The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution. Numerical simulations have shown that magnetic fields in the cores become supercritical and collapse\citep{Basu97}. In the process of  collapsing, an accretion disk is formed and significant magnetic flux is lost while the star also gradually loses its angular momentum. Powerful winds are magnetocentrifugally driven from the surface of the disk and turn into a jet-like flow due to magnetic hoops stresses \citep{Shu94}. This wind flows from the protostellar core and sweeps up gas into a massive molecular outflow. Massive stars form from massive cores, which are highly energised. These stars are highly luminous, therefore, they ionize their surrounding gas into HII regions. GMCs lose much of their original mass due to photo-evaporation. Most of the mass lost returns to the diffuse interstellar medium and completes the cycle of star formation, which then starts a new cycle (see \cite{McKee07} for more detail).

@@

In this paper, we present the observational review of measuring the star formation rate and other properties that affect measuring and scaling the SFR in nearby galaxies. In $\S2$ we discuss measuring the star formation rate. A discussion of the ISM is presented in $\S3$, followed by a discussion of the measurement of the stellar mass in $\S4$. In $\S5$ the KS law and the models for scaling the star formation rate are introduced. The current issues about KS law and the present project are discussed in $\S6$.

@@

Many groups have been trying to define a technique to calibrate emission from the newly-born, hot and massive ``€œO"€ and ``€œB"€ stars to the rate at which stars are being formed. Emission from the young massive stars are normally used as a tracer of the current SFR. Using luminosity of massive stars makes sense if one considers that star formation rate has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. The number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region. To do so, the stellar IMF must be known. However, knowing the Stellar IMF is not enough. To have a reliable SFR indicator, the stellar IMF must be fully sampled, which means that in the highest-mass bin at least one star is formed and all other mass bins have one or more stars (see section ~\ref{sec: imf}).

The ``O"€™ and ``€œB"€ stars can be observed by both using direct and indirect emission from stars; thus the SFR indicators are categorized based on these methods of observation. In the direct method, the SFR indicators can be probed by the ultraviolet (UV), optical, and near-infrared (NIR) emissions, while for probing the stellar light obscured by dust, mid/far-infrared emission is used. The ionizing photons are used in the indirect method. They are emitted by massive stars and traced by the ionized gas \citep[e.g.,][]{Calzetti04, Calzetti07}. In principle, the SFR is traced by the UV emission, the optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-millimetre range by using the Bremsstrahlung emission. Moreover, high mass binaries, massive stars and supernova explosions produce X-ray emissions which can be used as a tracer of star formation. Each of these tracers has some systematic errors, and one should decide which of these methods are more precise for a given system. for example using dust IR emission as an indicator is not precise in dwarf galaxies with small amounts of the gas, although still errors from dust extinction and attenuation must be considered (see section ~\ref{sec: ism}).

@@

In theory, for any system with high enough spatial resolution ($\sim 0.5- 1$ kpc), counting YSOs can be used as a tracer of the star formation. However, considering the limited capabilities of the present instrumentations, YSOs in most regions beyond the Magellanic clouds can not be resolved. Therefore, most studies use the emission from the ``O" and ``B" stars as tracer of the SFR. Another method to measure the SFR is by looking at the colour-magnitude diagram (CMD) of star-forming regions. \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to reproduce the spatially and age-resolved maps of star formation in nearby galaxies. More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to \citep{Kennicutt12}.

@@

Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the IR emission can be used to trace the SFR. The IR luminosity of a system depends not only on the amount of the embedded dust, but also on the heating rate provided by the stars. Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order the shape of the thermal IR SED depends on the starlight SED \citep{Helou86}. The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60  \mu$m) in comparison with the dust heated by old or low-mass stars.€“ Therefore, the IR wavelength is able to detect the emission from the young stellar population and be used as an SFR indicator.

@@

\section{Interstellar Medium}

@@

Considering the effects of the ISM on studying the SFR is important for two main reasons. First, stars are born from the gas; therefore, for scaling the star-formation rate in a galaxy, knowledge on the amount of gas is necessary. The other impact is that gas and dust in the ISM absorb the UV or optical emission from stars and re-emit it in the IR, or scatter the stellar light. Thus for tracing the star-forming region, the effect of dust must be taken into account, otherwise the SFR might be underestimated.

@@

 One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore. The other important advantage is that this method solves the newly-found problem of the "dark gas"€™ in the galaxies. Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}. So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter :stellar mass
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass}
\label{starmass}
One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. It was pointed out that stellar mass is linked with the structure and star formation history of disc galaxies \citep{Gavvazi96} and all morphologies \citep{Scodeggio02}. In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass \citep{Bell00}. \cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey \citep[SDSS;][]{York00}. They also showed that these results are applied for all morphological types.

@@

\section{Scaling the SFR Using Schmidt-Kennicut Law}

The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas. \cite{Schmidt59} assumed the constant IMF of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way. He scaled SFR with a power {\it n} of the gas mass, $M_{gas}$. Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$. A power law relation between surface densities of star formation and gas is known as the Schmidt law and is written as:
\begin{equation}
\Sigma_{SFR} \propto \Sigma_{gas}^n
\end{equation}
where $\Sigma_{SFR}$ is surface density of star formation, $\Sigma_{gas}$ is the surface density of gas in a galaxy and, {\it n} is the power index.

Following \cite{Schmidt59}, many groups worked on the scaling relation between the surface density of star formation, and the surface density of gas. \cite{Buat89} assumed the constant H$_2$/CO ratio and a \cite{Scalo86} initial mass function for the Milky Way. They measured SFR from the UV flux corrected and included molecular and atomic gas to derive the correlation between the star formation rate and the gas surface density. Another major work in that year was \cite{Kennicutt89}. By using H$\alpha$ emission for star formation, and HI and CO as a tracer of gas with constant H$_2$/CO, for more than 15 galaxies, he determined the average H$\alpha$ flux can be scaled with the average gas surface density to a power between 1 and 2.  To get better results he calculated star formation rate both as a function of galactocentric radius and averaged over whole galaxy disks. He also showed that the correlation is more accurate with using only HI as a tracer of gas.

A decade later, \cite{Kennicutt98a} examined another group of galaxies. He used H$\alpha$, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$. Using this power index, the Schmidt law can be rewritten as:

\begin{equation}
\Sigma_{SFR} \propto \Sigma_{gas}^{1.4\pm0.15}
\end{equation}
which is often referred to as the Kennicutt-Schmidt (KS) law.

In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution. For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$. He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$. He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
It should be noted that the KS law can not be applied for the whole range of gas densities. In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g. in regions far outside the optical disk \citep[e.g.,][]{Martin01, Bigiel08}

The Schmidt-Kennicutt scaling relation for star formation is valid for different types of galaxies both in the local universe \citep[e.g.,][]{Kennicutt98a, Bigiel08} and at high-Z \citep[e.g.,][]{Genzel10}, but it is strange that they only consider the effect of gas component while in reality various ISM and stellar objects affect the processes of formation of stars. Current proposed Schmidt relations, do not include the effects of metallicity \citep{Gnedin10}, dust grains, radiation shielding of H$_2$ regions \citep[for a review, see][]{Hollenbach99}, and stellar gravitational effects, as they only invoke the gas component.  Existing stars which form over the whole galaxy's life time are the reason for many of the processes mentioned above. As an example the gas angular momentum can be removed or nuclear SFRs can be increased by the gravitational effects of stellar bars in normal galaxies \citep[e.g.,][]{Sersic67}.

\cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density. Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges. \cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying on a large sample of galaxies. They showed this relation as a power law relation and referred to it as the extended Schmidt law:

\begin{equation}
\Sigma_{SFR} \propto \Sigma_{gas}^{\alpha} \Sigma_{star}^{\beta}
\end{equation}
where $\Sigma_{SFR}$ is SFR surface density, $\Sigma_{gas}$ and $\Sigma_{star}$ are gas mass and stellar surface density. $\alpha$ and $\beta$ are the power law indexes.  They showed that this relation not only predicts SFR as well as the KS law for galaxies and spatially resolved regions ($\sim$1 kpc sizes) where the KS law works, but also is acceptable for low surface brightness galaxies and regions where the KS law fails.

\begin{figure}[h]
\label{fig:duste}
\centering
\includegraphics[width=16cm]{../image_intro/schmidtvsextended}
\caption{Comparing The extended Schmidt law (a) and the Kennicutt-Schmidt relationship (b) for predicting the SFR. The solid and dotted lines are the best fit and observed 1-$\sigma$ scatter, respectively. The fit to the KS law (right panel) is done excluding LSB and early type galaxies. Adapted from \cite{Shi11}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter: current work
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Current issues and the Present Project}
\label{chap:mp}
Studying formation of stars helps us understand the formation and evolution of the universe. Since forming stars contains many complex physical processes, theoretical studies cannot yet give a complete picture of star formation. Therefore empirical studies are used to find scaling laws indicating, which parameters have effects on star formation. Between different scaling relations for star formation, the KS law is the most tested empirical star formation law. Since 1959, many studies have tested KS law on regions inside the Milky Way, nearby galaxies and high redshift galaxies. Not only observational studies, but also  simulations both apply and investigate KS law. Despite all these studies, there are still many unsolved questions about the KS law; Is it really a good correlation? What is the slope, and is it unique?, Does SFR surface density only scale with gas density? does the scatter affect by a second parameter(s)? What is the limit for applying the KS law? Is the SFR surface density correlation with total gas density stranger than with the H$_2$ surface density alone?

@@

The Andromeda galaxy is chosen for this project due to its similarity in the structure to the MW. Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "€œglobal"€ picture, whereas, studies of the MW are limited by our location within the Galaxy.  The Andromeda is closest spiral galaxy to the MW, therefore, we can have higher resolution images of it than we have of any other spiral galaxy. Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law. The KS law has been tested on the Andromeda galaxy many times but the results have been controversial. The range of slope of KS law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10, Ford13}. Testing extended Schmidt law on the Andromeda galaxy would help us recognise parameters that affect the star formation in the Andromeda galaxy and leads us to model and simulate star formation more accurately. Also it helps us answer questions about in what types of the regions (e.g. in case of different surface brightness, metallicity, distance from the disk, etc.) effect of the stellar mass is more important.

>>>>

\section{Overview}
Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe. Stars are also central to the formation of planetary systems and are where the ingredients for life were formed. The energy provided by stars is necessary to maintain the life on planets. The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System. This is one of the main reasons that the study of stellar structure and evolution has been a central topic in astronomy and astrophysics for decades.

@@

In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the interstellar medium (ISM) which is due to gravitational instabilities. The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution. Numerical simulations have shown that magnetic fields in the cores become super-critical and collapse\citep{Basu97}. In the process of  collapsing, an accretion disk is formed and significant magnetic flux is lost while the star also gradually loses its angular momentum. Powerful winds are magnetocentrifugally driven from the surface of the disk and turn into a jet-like flow due to magnetic hoops stresses \citep{Shu94}. This wind flows from the protostellar core and sweeps up gas into a massive molecular outflow. Massive stars form from massive cores, which are highly energised. These stars are highly luminous, therefore, they ionize their surrounding gas into \hii regions. GMCs lose much of their original mass due to photo-evaporation. Most of the mass lost returns to the diffuse interstellar medium and completes the cycle of star formation, which then starts a new cycle (see~\cite{McKee07} for more detail).

@@

In this chapter, we present the observational review of measuring the star formation rate and other properties that affect measuring and scaling the SFR in nearby galaxies. In $\S$~\ref{chap:sfr} we discuss measuring the star formation rate. A discussion of the ISM is presented in $\S$~\ref{chap:ISM}, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{chap:starrmass}. In $\S$~\ref{chap:metal} we talk about effect of metallicity on SFR. The current issues about studying star formation and its relation to other properties of a galaxy and the present project are discussed in $\S$~\ref{chap:cipp}.

@@

Many groups have been trying to define a technique to calibrate emission from the newly-born, hot and massive ``O'' and ``B'' stars to the rate at which stars are being formed. Emission from the young massive stars are normally used as a tracer of the current SFR. Using luminosity of massive stars makes sense if one considers that star formation rate has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. The number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region. To do so, the stellar IMF must be known. However, knowing the Stellar IMF is not enough. To have a reliable SFR indicator, the stellar IMF must be fully sampled, which means that in the highest-mass bin at least one star is formed and all other mass bins have one or more stars (see section ~\ref{sec: imf}).

The ``O'' and ``B'' stars can be observed by both using direct and indirect emission from stars; thus the SFR indicators are categorized based on these methods of observation. In the direct method, the SFR indicators can be probed by the ultraviolet (UV), optical, and near-infrared (NIR) emissions, while for probing the stellar light obscured by dust, mid/far-infrared emission is used. The ionizing photons are used in the indirect method. They are emitted by massive stars and traced by the ionized gas \citep[e.g.,][]{Calzetti04, Calzetti07}. In principle, the SFR is traced by the UV emission, the optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-millimetre range by using the Bremsstrahlung emission. Moreover, high mass binaries, massive stars and supernova explosions produce X-ray emissions which can be used as a tracer of star formation. Each of these tracers has some systematic errors, and one should decide which of these methods are more precise for a given system. for example using dust IR emission as an indicator is not precise in dwarf galaxies with small amounts of the gas, although still errors from dust extinction and attenuation must be considered (see section ~\ref{sec: ism}).

@@

In theory, for any system with high enough spatial resolution ($\sim 0.5- 1$ kpc), counting YSOs can be used as a tracer of the star formation. However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic clouds can not be resolved. Therefore, most studies use the emission from the ``O" and ``B" stars as tracer of the SFR. Another method to measure the SFR is by looking at the colour-magnitude diagram (CMD) of star-forming regions. \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to reproduce the spatially and age-resolved maps of star formation in nearby galaxies. More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to \citep{Kennicutt12}.

@@

Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the IR emission can be used to trace the SFR. The IR luminosity of a system depends not only on the amount of the embedded dust, but also on the heating rate provided by the stars. Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order the shape of the thermal IR SED depends on the starlight SED \citep{Helou86}. The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60  \mu$m) in comparison with the dust heated by old or low-mass stars.
Therefore, the IR wavelength is able to detect the emission from the young stellar population and be used as an SFR indicator.

@@

\section{Interstellar Medium}
\label{chap:ism}

@@

Considering the effects of the ISM on studying the SFR is important for two main reasons. First, stars are born from the gas; therefore, for scaling the star-formation rate in a galaxy, knowledge on the amount of gas is necessary. The other impact is that gas and dust in the ISM absorb the UV or optical emission from stars and re-emit it in the IR, or scatter the stellar light. Thus for tracing the star-forming region, the effect of dust must be taken into account, otherwise the SFR might be underestimated. 
\subsection{Molecular clouds}
\subsection{Ionized regions}
\subsection{Dust}

@@

 One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore. The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies. Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}. So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter :stellar mass
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass}
\label{chap:starmass}
One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. It was pointed out that stellar mass is linked with the structure and star formation history of disc galaxies \citep{Gavvazi96} and all morphologies \citep{Scodeggio02}. In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass \citep{Bell00}. \cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey \citep[SDSS;][]{York00}. They also showed that these results are applied for all morphological types.

@@

% \section{Scaling the SFR Using Schmidt-Kennicut Law}

% The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas. \cite{Schmidt59} assumed the constant IMF of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way. He scaled SFR with a power {\it n} of the gas mass, $M_{gas}$. Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$. A power law relation between surface densities of star formation and gas is known as the Schmidt law and is written as:
% \begin{equation}
% \Sigma_{SFR} \propto \Sigma_{gas}^n
% \end{equation}
% where $\Sigma_{SFR}$ is surface density of star formation, $\Sigma_{gas}$ is the surface density of gas in a galaxy and, {\it n} is the power index.

% Following \cite{Schmidt59}, many groups worked on the scaling relation between the surface density of star formation, and the surface density of gas. \cite{Buat89} assumed the constant H$_2$/CO ratio and a \cite{Scalo86} initial mass function for the Milky Way. They measured SFR from the UV flux corrected and included molecular and atomic gas to derive the correlation between the star formation rate and the gas surface density. Another major work in that year was \cite{Kennicutt89}. By using H$\alpha$ emission for star formation, and HI and CO as a tracer of gas with constant H$_2$/CO, for more than 15 galaxies, he determined the average H$\alpha$ flux can be scaled with the average gas surface density to a power between 1 and 2.  To get better results he calculated star formation rate both as a function of galactocentric radius and averaged over whole galaxy disks. He also showed that the correlation is more accurate with using only HI as a tracer of gas.

% A decade later, \cite{Kennicutt98a} examined another group of galaxies. He used H$\alpha$, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$. Using this power index, the Schmidt law can be rewritten as:

% \begin{equation}
% \Sigma_{SFR} \propto \Sigma_{gas}^{1.4\pm0.15}
% \end{equation}
% which is often referred to as the Kennicutt-Schmidt (KS) law.

% In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution. For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$. He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$. He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
% It should be noted that the KS law can not be applied for the whole range of gas densities. In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g. in regions far outside the optical disk \citep[e.g.,][]{Martin01, Bigiel08}

% The Schmidt-Kennicutt scaling relation for star formation is valid for different types of galaxies both in the local universe \citep[e.g.,][]{Kennicutt98a, Bigiel08} and at high-Z \citep[e.g.,][]{Genzel10}, but it is strange that they only consider the effect of gas component while in reality various ISM and stellar objects affect the processes of formation of stars. Current proposed Schmidt relations, do not include the effects of metallicity \citep{Gnedin10}, dust grains, radiation shielding of H$_2$ regions \citep[for a review, see][]{Hollenbach99}, and stellar gravitational effects, as they only invoke the gas component.  Existing stars which form over the whole galaxy's life time are the reason for many of the processes mentioned above. As an example the gas angular momentum can be removed or nuclear SFRs can be increased by the gravitational effects of stellar bars in normal galaxies \citep[e.g.,][]{Sersic67}.

% \cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density. Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges. \cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying on a large sample of galaxies. They showed this relation as a power law relation and referred to it as the extended Schmidt law:

% \begin{equation}
% \Sigma_{SFR} \propto \Sigma_{gas}^{\alpha} \Sigma_{star}^{\beta}
% \end{equation}
% where $\Sigma_{SFR}$ is SFR surface density, $\Sigma_{gas}$ and $\Sigma_{star}$ are gas mass and stellar surface density. $\alpha$ and $\beta$ are the power law indexes.  They showed that this relation not only predicts SFR as well as the KS law for galaxies and spatially resolved regions ($\sim$1 kpc sizes) where the KS law works, but also is acceptable for low surface brightness galaxies and regions where the KS law fails.

% \begin{figure}[h]
% \label{fig:duste}
% \centering
% \includegraphics[width=16cm]{../image_intro/schmidtvsextended}
% \caption{Comparing The extended Schmidt law (a) and the Kennicutt-Schmidt relationship (b) for predicting the SFR. The solid and dotted lines are the best fit and observed 1-$\sigma$ scatter, respectively. The fit to the KS law (right panel) is done excluding LSB and early type galaxies. Adapted from \cite{Shi11}.}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %chapter: current work
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Current issues and the Present Project}
 \label{chap:cipp}
 Studying formation of stars helps us understand the formation and evolution of the universe. Since forming stars contains many complex physical processes, theoretical studies cannot yet give a complete picture of star formation. Therefore empirical studies are used to find scaling laws indicating, which parameters have effects on star formation. Between different scaling relations for star formation, the KS law is the most tested empirical star formation law. Since 1959, many studies have tested KS law on regions inside the Milky Way, nearby galaxies and high redshift galaxies. Not only observational studies, but also  simulations both apply and investigate KS law. Despite all these studies, there are still many unsolved questions about the KS law; Is it really a good correlation? What is the slope, and is it unique?, Does SFR surface density only scale with gas density? does the scatter affect by a second parameter(s)? What is the limit for applying the KS law? Is the SFR surface density correlation with total gas density stranger than with the H$_2$ surface density alone?

@@

The Andromeda galaxy is chosen for this project due to its similarity in the structure to the MW. Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "global" picture, whereas, studies of the MW are limited by our location within the Galaxy.  The Andromeda is closest spiral galaxy to the MW, therefore, we can have higher resolution images of it than we have of any other spiral galaxy. Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law. The KS law has been tested on the Andromeda galaxy many times but the results have been controversial. The range of slope of KS law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10, Ford13}. Testing extended Schmidt law on the Andromeda galaxy would help us recognise parameters that affect the star formation in the Andromeda galaxy and leads us to model and simulate star formation more accurately. Also it helps us answer questions about in what types of the regions (e.g. in case of different surface brightness, metallicity, distance from the disk, etc.) effect of the stellar mass is more important.
